---
title: "Popularity"
output:
  html_document:
    theme: journal
---
```{r global, include = FALSE}
#load data
final <- readRDS("/Volumes/LaCie Rugged/Tweets/final_master_tweets.rds")
hashtag_dfm <- readRDS("/Volumes/LaCie Rugged/Tweets/hash_dfm.rds")
handles <- read.csv("/Volumes/LaCie Rugged/Tweets/master_handles.csv")
handles <- handles[,-1]
palette <- c("#004C99", "#336600", "#990000", "#CC6600", "#000000", "#006666", "#000066", "#330066", "#660066", "#660033", "#606060", "#003366", "#666600")
```

## Average Number of Followers by Party
```{r, echo = FALSE, warning = FALSE}
##TABLE OF AVERAGE # OF FOLLOWERS WITHIN EACH PARTY
followers <- final %>%
  filter(!screen_name %in% c("JustinTrudeau", "AndrewScheer", "ElizabethMay", "theJagmeetSingh", "MaximeBernier")) %>%
  group_by(screen_name, party, riding, province) %>%
  summarize(followers = max(followers_count, na.rm = T))

party_followers<- followers %>%
  filter(!is.na(party)) %>%
  group_by(party) %>%
  summarize(mean_followers = round(mean(followers, na.rm = T))) %>%
  arrange(desc(mean_followers))

datatable(party_followers, options = list(
  pageLength = 5, autoWidth = TRUE
),
class = 'cell-border stripe',
colnames = c('Party', 'Average # of Followers'))
```

## Average Number of Followers by Party and Gender
```{r, echo = FALSE, warning = FALSE}
##AVG # OF FOLLOWERS BY PARTY AND GENDER
followers_gndr <- final %>%
  group_by(screen_name, gender, party, riding, province) %>%
  filter(!screen_name %in% c("JustinTrudeau", "AndrewScheer", "ElizabethMay", "theJagmeetSingh", "MaximeBernier")) %>%
  summarize(followers = max(followers_count, na.rm = T))

party_followers_gndr <- followers_gndr %>%
  filter(!is.na(party), !is.na(gender)) %>%
  group_by(party, gender) %>%
  summarize(mean_followers = round(mean(followers, na.rm = T))) %>%
  arrange(desc(mean_followers))

datatable(party_followers_gndr, options = list(
  pageLength = 10, autoWidth = TRUE
),
class = 'cell-border stripe',
colnames = c('Party', 'Gender','Average # of Followers'))
```

## Influencers: Top Users With the Most Followers
```{r, echo = FALSE, warning = FALSE}
followers_user <- final %>%
  group_by(screen_name, gender, party, riding, province) %>%
  summarize(followers = max(followers_count, na.rm = T)) %>%
  arrange(desc(followers))

datatable(followers_user, filter = 'top', options = list(
  pageLength = 10, autoWidth = TRUE
),
class = 'cell-border stripe',
colnames = c('Screen Name', 'Gender', 'Party','Riding','Province', '# of Followers'))
```

## Tweet Appeal: Who Gets the Most 'Favourites'?
#### Among All Candidates
```{r, echo = FALSE, warning = FALSE}
favs_user <- final %>%
  group_by(screen_name, gender, party, riding, province) %>%
  summarize(favourites = round(mean(favorite_count, na.rm = T))) %>%
  arrange(desc(favourites))

datatable(favs_user, filter = 'top', options = list(
  pageLength = 10, autoWidth = TRUE
),
class = 'cell-border stripe',
colnames = c('Screen Name', 'Gender', 'Party','Riding','Province', 'Average # of Favourites'))
```

#### By Party and Gender
```{r, echo = FALSE, warning = FALSE}
favs_party_gndr <- favs_user %>%
  filter(!is.na(party), !is.na(gender)) %>%
  group_by(party, gender) %>%
  summarize(favourites = round(mean(favourites, na.rm = T))) %>%
  arrange(desc(favourites))

datatable(favs_party_gndr, filter = 'top', options = list(
  pageLength = 10, autoWidth = TRUE
),
class = 'cell-border stripe',
colnames = c("Party", "Gender", "Average # of Favourites"))
```

## Tweet Appeal: What about Retweets?
#### Among All Candidates
```{r, echo = FALSE, warning = FALSE}
rts_user <- final %>%
  group_by(screen_name, gender, party, riding, province) %>%
  summarize(rts = round(mean(retweet_count, na.rm = T))) %>%
  arrange(desc(rts))

datatable(rts_user, filter = 'top', options = list(
  pageLength = 10, autoWidth = TRUE
),
class = 'cell-border stripe',
colnames = c('Screen Name', 'Gender', 'Party','Riding','Province', 'Average Number of Retweets per Tweet'))
```

#### By Party and Gender
```{r, echo = FALSE, warning = FALSE}
rts_party_gndr <- rts_user %>%
  filter(!is.na(party), !is.na(gender)) %>%
  group_by(party, gender) %>%
  summarize(rts = round(mean(rts, na.rm = T))) %>%
  arrange(desc(rts))

datatable(rts_party_gndr, filter = 'top', options = list(
  pageLength = 10, autoWidth = TRUE
),
class = 'cell-border stripe',
colnames = c("Party", "Gender", "Average # of Retweets per Tweet"))
```


- table: top 10 users with highest average likes in each party
- table: top 10 users with highest average retweets in each party


