---
title: "Trending Issues"
output:
  html_document:
    theme: journal
---
```{r global, include = FALSE}
#load data
final <- readRDS("/Volumes/LaCie Rugged/Tweets/final_master_tweets.rds")
hashtag_dfm <- readRDS("/Volumes/LaCie Rugged/Tweets/hash_dfm.rds")
handles <- read.csv("/Volumes/LaCie Rugged/Tweets/master_handles.csv")
handles <- handles[,-1]
palette <- c("#004C99", "#336600", "#990000", "#CC6600", "#000000", "#006666", "#000066", "#330066", "#660066", "#660033", "#606060", "#003366", "#666600")
```

## Overview of Popular Hashtags
### Overall
```{r, echo = FALSE, warning = FALSE, fig.align="center", fig.width=6, fig.height=6, fig.cap="Note: top two hashtags #cdnpoli and #elxn43 have been removed"}
set.seed(132)
textplot_wordcloud(hashtag_dfm, max_words = 100)
```

### By Party
#### The Conservatives
```{r, echo = FALSE, warning = FALSE, fig.align="center", fig.width=6, fig.height=6, fig.cap="Note: top two hashtags #cdnpoli and #elxn43 have been removed"}
hash_dfm_cpc <- readRDS("/Volumes/LaCie Rugged/Tweets/hash_dfm_cpc.rds")
textplot_wordcloud(hash_dfm_cpc, max_words = 100,
                   color = "steelblue4")
```

#### The Liberals
```{r, echo = FALSE, warning = FALSE, fig.align="center", fig.width=6, fig.height=6, fig.cap="Note: top two hashtags #cdnpoli and #elxn43 have been removed"}
hash_dfm_lpc <- readRDS("/Volumes/LaCie Rugged/Tweets/hash_dfm_lpc.rds")
textplot_wordcloud(hash_dfm_lpc, max_words = 100,
                   color = "firebrick4")
```

#### The New Democrats
```{r, echo = FALSE, warning = FALSE, fig.align="center", fig.width=6, fig.height=6, fig.cap="Note: top two hashtags #cdnpoli and #elxn43 have been removed"}
hash_dfm_ndp <- readRDS("/Volumes/LaCie Rugged/Tweets/hash_dfm_ndp.rds")
textplot_wordcloud(hash_dfm_ndp, max_words = 100,
                   color = "darkorange3")
```

#### The Greens
```{r, echo = FALSE, warning = FALSE, fig.align="center", fig.width=6, fig.height=6, fig.cap="Note: top two hashtags #cdnpoli and #elxn43 have been removed"}
hash_dfm_gpc <- readRDS("/Volumes/LaCie Rugged/Tweets/hash_dfm_gpc.rds")
textplot_wordcloud(hash_dfm_gpc, max_words = 100,
                   color = "darkolivegreen4")
```

#### The People's Party
```{r, echo = FALSE, warning = FALSE, fig.align="center", fig.width=6, fig.height=6, fig.cap="Note: top two hashtags #cdnpoli and #elxn43 have been removed"}
hash_dfm_ppc <- readRDS("/Volumes/LaCie Rugged/Tweets/hash_dfm_ppc.rds")
textplot_wordcloud(hash_dfm_ppc, max_words = 100,
                   color = "gray0")
```

## Top Words Used by Each Party
#### Keywords, not hashtags
```{r, echo = FALSE, warning = FALSE}
#textstat_frequency(dfm_en, n = 10, groups = "party")
#need to do this through the cleaning and preprocessing script
```



- then broken down by gender
- top hashtags by party
- prevalence of talking about key issues by party and gender (tweets on each key topic)
- keyness analysis -- unique words used within each issue type by party
