---
title: "Tweet Volume & Activity"
output:
  html_document:
    theme: journal
---
```{r global, include = FALSE}
#load data
final <- readRDS("/Volumes/LaCie Rugged/Tweets/final_master_tweets.rds")
hashtag_dfm <- readRDS("/Volumes/LaCie Rugged/Tweets/hash_dfm.rds")
handles <- read.csv("/Volumes/LaCie Rugged/Tweets/master_handles.csv")
handles <- handles[,-1]
palette <- c("#004C99", "#336600", "#990000", "#CC6600", "#000000", "#006666", "#000066", "#330066", "#660066", "#660033", "#606060", "#003366", "#666600")
```

```{r setup, include=FALSE}
library(tidyverse)
library(tidytext)
library(plotly)
library(knitr)
library(textstem)
library(quanteda)
library(DT)
```

## Total Volume of Candidate Tweets By Party and Week
#### Since March 2019
```{r, echo = FALSE, warning = FALSE}
###STILL NEED TO ADD KEY EVENTS!! FROM MAX LIST##
##OVERALL VOLUME OF CANDIDATE TWEETS BY PARTY
palette <- c("#004C99", "#336600", "#990000", "#CC6600", "#000000")

Volume <- final %>%
  group_by(party, week_range) %>%
  summarise(volume = length(text)) %>%
  na.omit(cols = c("party", "week_range")) %>%
  ungroup()

Volume %>%
  mutate(text_label = str_c("Volume:", volume, '\nWeek: ', week_range)) %>% 
  plot_ly(x = ~week_range, y = ~volume, type = "scatter", mode = "lines",
          alpha = 0.5,
          text = ~text_label,
          color = ~party,
          colors = palette)%>%
  layout(title = "Volume of Tweets Per Week by Party: March 4th to Present",
         xaxis = list(title = "Week"),
         yaxis = list(title = "Total Number Tweets"))
```


## Total Volume of Candidate **Retweets** by Party and Week
```{r, echo = FALSE, warning = FALSE}
##RETWEETS OVER TIME BY PARTY
palette <- c("#004C99", "#336600", "#990000", "#CC6600", "#000000")

vol_rts <- final %>%
  group_by(party, week_range) %>%
  filter(is_retweet == TRUE) %>%
  summarise(volume_rts = length(text)) %>%
  na.omit(cols = c("party", "week_range")) %>%
  ungroup()

vol_rts %>%
  mutate(text_label = str_c("Volume:", volume_rts, '\nWeek: ', week_range)) %>% 
  plot_ly(x = ~week_range, y = ~volume_rts, type = "scatter", mode = "lines",
          alpha = 0.5,
          text = ~text_label,
          color = ~party,
          colors = palette)%>%
  layout(title = "Volume of Retweets Per Week by Party: March 4th to Present",
         xaxis = list(title = "Week"),
         yaxis = list(title = "Total Number of Retweets"))

```


## Total Volume of Candidate **Self-Authored Tweets** by Party and Week
```{r, echo = FALSE, warning = FALSE}
##SELF-AUTHORED OVER TIME BY PARTY
palette <- c("#004C99", "#336600", "#990000", "#CC6600", "#000000")

vol_sa <- final %>%
  group_by(party, week_range) %>%
  filter(is_retweet == FALSE) %>%
  summarise(volume_sa = length(text)) %>%
  na.omit(cols = c("party", "week_range")) %>%
  ungroup()

vol_sa %>%
  mutate(text_label = str_c("Volume:", volume_sa, '\nWeek: ', week_range)) %>% 
  plot_ly(x = ~week_range, y = ~volume_sa, type = "scatter", mode = "lines",
          alpha = 0.5,
          text = ~text_label,
          color = ~party,
          colors = palette)%>%
  layout(title = "Volume of Self-Authored Per Week by Party: March 4th to Present",
         xaxis = list(title = "Week"),
         yaxis = list(title = "Total Number of Self-Authored Tweets"))

```

## Investigating Gender Differences in Tweet Type
#### Across all parties
```{r, echo = FALSE, warning = FALSE}
##WHO WRITES MORE SELF-AUTHORED TWEETS -- MEN OR WOMEN?
vol_gender <- final %>%
  group_by(gender, week_range, is_retweet) %>%
  summarise(volume_gndr = length(text)) %>%
  na.omit(cols = c("gender", "week_range")) %>%
  ungroup()

vol_gender %>%
  mutate(text_label = str_c("Volume:", volume_gndr, '\nWeek: ', week_range)) %>% 
  plot_ly(x = ~week_range, y = ~volume_gndr, type = "scatter", mode = "lines",
          alpha = 0.5,
          text = ~text_label,
          color = ~gender,
          symbol = ~is_retweet,
          colors = palette)%>%
  layout(title = "Volume of Tweets Per Week by Gender and RT Status: March 4th to Present",
         xaxis = list(title = "Week"),
         yaxis = list(title = "Total Number of Tweets"))
```

```{r, echo = FALSE, warning = FALSE, include = FALSE}
glm(data = final, is_retweet ~ gender + party, family = binomial)
summary(glm(data = final, is_retweet ~ gender + party, family = binomial))
```

## Party-Level Differences Between Men's and Women's Tweet Types
#### Conservative Party 
```{r, echo = FALSE, warnings = FALSE}
##AND ARE THERE ANY PARTY-LEVEL GENDER DISCREPENCIES THAT STAND OUT?
#CPC
type_cpc <- final %>%
  filter(party == "CPC", !is.na(gender)) %>%
  mutate(rt_status = ifelse(is_retweet == "TRUE", "Retweet", "Self-Authored")) %>%
  filter(!is.na(rt_status)) %>%
  ggplot(aes(x=gender, fill=rt_status)) +
    geom_bar(position="fill", colour="black") +
    scale_fill_manual(values= c("gray70", "pink4")) +
  labs(x = "Gender",
       y = "Proportion of Tweets Under each Type",
       fill = "Tweet Type",
       title = 'Prevalence of CPC Candidate Tweet Type by Gender')
ggplotly(type_cpc)
```

#### Liberal Party 
```{r, echo = FALSE, warnings = FALSE}
#LPC
type_lpc <- final %>%
  filter(party == "LPC", !is.na(gender)) %>%
  mutate(rt_status = ifelse(is_retweet == "TRUE", "Retweet", "Self-Authored")) %>%
  filter(!is.na(rt_status)) %>%
  ggplot(aes(x=gender, fill=rt_status)) +
    geom_bar(position="fill", colour="black") +
    scale_fill_manual(values= c("gray70", "pink4")) +
  labs(x = "Gender",
       y = "Proportion of Tweets Under each Type",
       fill = "Tweet Type",
       title = 'Prevalence of LPC Candidate Tweet Type by Gender')
ggplotly(type_lpc)
```

#### New Democratic Party
```{r, echo = FALSE, warnings = FALSE}
#NDP
type_ndp <- final %>%
  filter(party == "NDP", !is.na(gender)) %>%
  mutate(rt_status = ifelse(is_retweet == "TRUE", "Retweet", "Self-Authored")) %>%
  filter(!is.na(rt_status)) %>%
  ggplot(aes(x=gender, fill=rt_status)) +
    geom_bar(position="fill", colour="black") +
    scale_fill_manual(values= c("gray70", "pink4")) +
  labs(x = "Gender",
       y = "Proportion of Tweets Under each Type",
       fill = "Tweet Type",
       title = 'Prevalence of NDP Candidate Tweet Type by Gender')
ggplotly(type_ndp)
```

#### Green Party
```{r, echo = FALSE, warnings = FALSE}
#GPC
type_gpc <- final %>%
  filter(party == "GPC", !is.na(gender)) %>%
  mutate(rt_status = ifelse(is_retweet == "TRUE", "Retweet", "Self-Authored")) %>%
  filter(!is.na(rt_status)) %>%
  ggplot(aes(x=gender, fill=rt_status)) +
    geom_bar(position="fill", colour="black") +
    scale_fill_manual(values= c("gray70", "pink4")) +
  labs(x = "Gender",
       y = "Proportion of Tweets Under each Type",
       fill = "Tweet Type",
       title = 'Prevalence of GPC Candidate Tweet Type by Gender')
ggplotly(type_gpc)
```

#### People's Party of Canada
```{r, echo = FALSE, warnings = FALSE}
#PPC
type_ppc <- final %>%
  filter(party == "PPC", !is.na(gender)) %>%
  mutate(rt_status = ifelse(is_retweet == "TRUE", "Retweet", "Self-Authored")) %>%
  filter(!is.na(rt_status)) %>%
  ggplot(aes(x=gender, fill=rt_status)) +
    geom_bar(position="fill", colour="black") +
    scale_fill_manual(values= c("gray70", "pink4")) +
  labs(x = "Gender",
       y = "Proportion of Tweets Under each Type",
       fill = "Tweet Type",
       title = 'Prevalence of PPC Candidate Tweet Type by Gender')
ggplotly(type_ppc)
```

## Overall Tweet-Volume (self-authored and retweets) by Candidate Gender and Party
```{r, echo = FALSE, warning = FALSE}
###TWEET VOLUME BY GENDER AND PARTY
vol <- final %>%
  filter(!is.na(gender)) %>%
  group_by(party, gender) %>%
  summarize(n = n_distinct(screen_name),
            Volume = length(!is.na(text)),
            Avg_Per_User = round(Volume/n))

datatable(vol, filter = 'top', options = list(
  pageLength = 10, autoWidth = TRUE
),
class = 'cell-border stripe',
colnames = c('Party', 'Gender', '# of Candidates', 'Overall Volume', 'Average Tweets per User'))
```

## The Eager-Beavers: Overall Highest-Volume Tweeters
```{r, echo = FALSE, warning = FALSE}
###OVERALL HIGHEST VOLUME TWEETERS
highest.vol <- final %>%
  group_by(screen_name, name, party, gender, riding, province) %>%
  summarize(count = length(text)) %>%
  arrange(desc(count))

datatable(highest.vol, filter = 'top', options = list(
  pageLength = 10, autoWidth = TRUE
),
class = 'cell-border stripe',
colnames = c('Handle','Name','Party','Gender', 'Riding', 'Province', 'Total Tweets'))
```

## Highest-Volume Tweeters by Party
#### Conservative Party
```{r, echo = FALSE, warning = FALSE}
###HIGHEST VOLUME TWEETERS BY PARTY
#CPC
cpc_highvol <- final %>%
  filter(party == "CPC") %>%
  group_by(screen_name, name, gender, riding, province) %>%
  summarize(count = length(text)) %>%
  arrange(desc(count))

datatable(cpc_highvol, filter = 'top', options = list(
  pageLength = 10, autoWidth = TRUE
),
class = 'cell-border stripe',
colnames = c('Handle','Name', 'Gender', 'Riding', 'Province', 'Total Tweets'))
```

#### The Liberals
```{r, echo = FALSE, warning = FALSE}
#LPC
lpc_highvol <- final %>%
  filter(party == "LPC") %>%
  group_by(screen_name, name, gender, riding, province) %>%
  summarize(count = length(text)) %>%
  arrange(desc(count))

datatable(lpc_highvol, filter = 'top', options = list(
  pageLength = 10, autoWidth = TRUE
),
class = 'cell-border stripe',
colnames = c('Handle','Name', 'Gender', 'Riding', 'Province', 'Total Tweets'))
```

#### The New Democratic Party
```{r, echo = FALSE, warning = FALSE}
#NDP
ndp_highvol <- final %>%
  filter(party == "NDP") %>%
  group_by(screen_name, name, gender, riding, province) %>%
  summarize(count = length(text)) %>%
  arrange(desc(count))

datatable(ndp_highvol, filter = 'top', options = list(
  pageLength = 10, autoWidth = TRUE
),
class = 'cell-border stripe',
colnames = c('Handle','Name', 'Gender', 'Riding', 'Province', 'Total Tweets'))
```

#### The Green Party
```{r, echo = FALSE, warning = FALSE}
#GPC
gpc_highvol <- final %>%
  filter(party == "GPC") %>%
  group_by(screen_name, name, gender, riding, province) %>%
  summarize(count = length(text)) %>%
  arrange(desc(count))

datatable(gpc_highvol, filter = 'top', options = list(
  pageLength = 10, autoWidth = TRUE
),
class = 'cell-border stripe',
colnames = c('Handle','Name', 'Gender', 'Riding', 'Province', 'Total Tweets'))
```

#### The People's Party of Canada
```{r, echo = FALSE, warning = FALSE}
#PPC
ppc_highvol <- final %>%
  filter(party == "PPC") %>%
  group_by(screen_name, name, gender, riding, province) %>%
  summarize(count = length(text)) %>%
  arrange(desc(count))

datatable(ppc_highvol, filter = 'top', options = list(
  pageLength = 10, autoWidth = TRUE
),
class = 'cell-border stripe',
colnames = c('Handle','Name', 'Gender', 'Riding', 'Province', 'Total Tweets'))
```

